Towards a Practical Face Recognition System: \\ Robust Alignment and Illumination by Sparse Representation

### 2011-04-05 faces_system.tex
Working on bios

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{bios/arvind}}]{Andrew Wagner}
Andrew Wagner received his Bachelor's degree in General Engineering,
and his Master's degree in Electrical Engineering, from the University
of Illinois at Urbana-Champaign, where he is currently a Ph.D.
candidate in Electrical \& Computer Engineering.
His research interests include robotics, computer vision, and optimal control.
His recent work focuses on parallel algorithms for sparsity
based face recognition.\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{bios/arvind}}]{John Wright}
Arvind Ganesh received his Bachelor's and Master's degrees, both in Electrical
Engineering, from the Indian Institute of Technology, Madras, India in 2006. He
is currently a PhD candidate in the Electrical \& Computer Engineering
Department at the University of Illinois, Urbana-Champaign. His research
interests include compressed sensing, computer vision, and machine learning.
His recent work focuses on low-rank matrix recovery techniques for
batch image alignment and texture rectification.  \end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{bios/arvind}}]{Arvind Ganesh}
Arvind Ganesh received his Bachelor's and Master's degrees, both in Electrical
Engineering, from the Indian Institute of Technology, Madras, India in 2006. He
is currently a PhD candidate in the Electrical \& Computer Engineering
Department at the University of Illinois, Urbana-Champaign. His research
interests include compressed sensing, computer vision, and machine learning.
His recent work focuses on low-rank matrix recovery techniques for
batch image alignment and texture rectification.  \end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{bios/arvind}}]{Zihan Zhou}
Arvind Ganesh received his Bachelor's and Master's degrees, both in Electrical
Engineering, from the Indian Institute of Technology, Madras, India in 2006. He
is currently a PhD candidate in the Electrical \& Computer Engineering
Department at the University of Illinois, Urbana-Champaign. His research
interests include compressed sensing, computer vision, and machine learning.
His recent work focuses on low-rank matrix recovery techniques for
batch image alignment and texture rectification.  \end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{bios/arvind}}]{Hossein Mobahi}
Arvind Ganesh received his Bachelor's and Master's degrees, both in Electrical
Engineering, from the Indian Institute of Technology, Madras, India in 2006. He
is currently a PhD candidate in the Electrical \& Computer Engineering
Department at the University of Illinois, Urbana-Champaign. His research
interests include compressed sensing, computer vision, and machine learning.
His recent work focuses on low-rank matrix recovery techniques for
batch image alignment and texture rectification.  \end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{bios/arvind}}]{Yi Ma}
Arvind Ganesh received his Bachelor's and Master's degrees, both in Electrical
Engineering, from the Indian Institute of Technology, Madras, India in 2006. He
is currently a PhD candidate in the Electrical \& Computer Engineering
Department at the University of Illinois, Urbana-Champaign. His research
interests include compressed sensing, computer vision, and machine learning.
His recent work focuses on low-rank matrix recovery techniques for
batch image alignment and texture rectification.  \end{IEEEbiography}

% if you will not have a photo
%\begin{biographynophoto}{John Doe}
%Biography text here.
%\end{biographynophoto}

>>>>

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{bios/drew}}]{Andrew Wagner}
received his Bachelor's degree in General Engineering in 2003,
and his Master's degree in Electrical Engineering in 2006, from the University
of Illinois at Urbana-Champaign, where he is currently a Ph.D.
candidate in Electrical \& Computer Engineering.
His research interests include robotics, computer vision, and optimal control.
His recent work focuses on parallel algorithms for sparsity
based face recognition.\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{bios/john}}]{John
Wright} received his PhD in Electrical Engineering from the
University of Illinois at Urbana-Champaign in October 2009. He is currently a
researcher in the Visual Computing group at Microsoft Research Asia.  His
research focuses on developing provably correct and efficient tools for
recovering low-dimensional structure in corrupted high-dimensional datasets.
His work has received a number of awards, including the 2009 Lemelson-Illinois
Prize for Innovation, the 2009 UIUC Martin Award for Excellence in Graduate
Research, a 2008-2010 Microsoft Research Fellowship, a Carver fellowship, and a
UIUC Bronze Tablet award.  \end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{bios/arvind}}]{Arvind Ganesh}
received his Bachelor's and Master's degrees, both in Electrical
Engineering, from the Indian Institute of Technology, Madras, India in 2006. He
is currently a PhD candidate in the Electrical \& Computer Engineering
Department at the University of Illinois, Urbana-Champaign. His research
interests include compressed sensing, computer vision, and machine learning.
His recent work focuses on low-rank matrix recovery techniques for
batch image alignment and texture rectification.  \end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{bios/arvind}}]{Zihan Zhou}
received... {\bf PLACEHOLDER}
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{bios/arvind}}]{Hossein Mobahi}
received... {\bf PLACEHOLDER}
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{bios/yi}}]{Yi
Ma} received two Bachelors degree in Automation and Applied Mathematics
from  Tsinghua University, Beijing, China, in 1995. He received an Master
degree in Electrical Engineering and Computer Sciences (EECS) in 1997, a second
Master degree in Mathematics in 2000, and the Ph.D. degree in EECS in 2000, all
from the University of California at Berkeley. He is currently an associate
professor (with tenure) at the Department of Electrical and Computer
Engineering, University of Illinois at Urbana-Champaign, and since January 2009
has also served as research manager for the Visual Computing Group at Microsoft
Research Asia, Beijing, China.  \end{IEEEbiography}

%He is an associate
%editor of the  IEEE Transactions on Pattern Analysis and Machine Intelligence
%since 2007 and the International Journal of Computer Vision since 2010. He has
%also served as the chief guest editor for special issues for the Proceedings of
%IEEE and the IEEE Signal Processing Magazine. He serves as Area Chair for NIPS
%2011, Program Board Memember for ICCV 2011, and Program Chair for ICCV 2013.

% if you will not have a photo
%\begin{biographynophoto}{John Doe} Biography text here.
%\end{biographynophoto}
